% LINKS
% https://cpd.suny.edu/surc/proposal-information/
% https://www.buffalo.edu/eln/students/project-portal/funding/funding1.html -- ELN FUNDING
%

\documentclass[12pt]{article}

% Packages
\usepackage{amsmath}

% Document
\begin{document}
 GUIDELINES
    \textbf{Abstract submissions should be:}
    \begin{itemize}
    \item Written clearly and concisely
    \item Identify the central research question, objective, or thesis of the project.
    \item Summarize the methodology and/or findings of the research or creative work.
    \item State conclusions, significance, and/or current state of the project
    \item Written at college level (e.g., spelling, grammar, clarity, etc.)
    \item Have prior approval by all secondary authors and the SUNY faculty mentor (faculty mentors will be notified via email of your submission).
    \item Creative proposals should include an explanation of what motivated or inspired the work and what the audience is expected to experience when they view the work.
    \end{itemize}

    \textbf{Abstract Formatting Guidelines:}

    \begin{itemize}
    \item Titles should be \textbf{bolded}, short and specific, and in mixed UPPER- and lower-case letters.
    \item Use a 12-point Times New Roman font.
    \item Abstract must be between 200 to 250 words (maximum).
    \item Include plain text only. \textbf{DO NOT} include tables, charts, pictures, foreign characters, or scientific symbols.
    \item \textbf{DO NOT}include citations and a reference list, unless a reference is central to the work being presented. (In this case, include the reference parenthetically in the body of the abstract.)
    \item The title and abstract will appear in the conference program exactly as submitted, so please double-check spelling, punctuation, and clarity of prose.
    \end{itemize}


    \textbf{Abstract Submission Information:}

    Please have the following information readily available when submitting your abstract/proposal:\begin{itemize}
    \item Primary presenter name, e-mail address, phone number, college/university, academic field
    \item Faculty mentor name, college/university name, and e-mail address
    \item If appropriate, co-presenter(s) name(s) and e-mail address(es)
    \item If appropriate, secondary author(s) name(s) and e-mail address(es)
    \item Presentation type: Poster Presentation, Oral Presentation, Exhibit/Performance
    \item Presentation title
    \item Abstract (between 200-250 words)
    \item Special equipment or space requests
    \end{itemize}

\pagebreak




\end{document}